Objective-First Nanophotonic Design Plan

### 2012-12-18 plan/plan.tex
Corrected global paradigm math.

\subsubsection{Relaxation of $f_i(x_i)$}
In order to compute $\Delta x_i$ we relax the design objectives, $f_i(x_i)$, to a differentiable, and convex form.
Specifically, the upper bound constraint is relaxed via
    \E{}{I_+(\beta_{ij} - |c\T_{ij} x_i|) \to -\frac{1}{t} \ln (\beta_{ij}^2 - \norm{c\T_{ij} x_i}^2),}
    where $t$ is a real positive scalar. The lower bound constraint is relaxed via
    \E{}{I_+(|c\T_{ij} x_i| - \alpha_{ij}) \to -\frac{1}{t} \ln (\real[e^{i\phi}c\T_{ij} x_i] - \alpha_{ij}),}
     where $e^{i\phi}$ is a phase factor on $c\T_{ij} x_i$.

The gradient can now be obtained as
% \footnote{
%     \EE{}{\grad_{x_i} f_i(x_i) &= \frac{1}{t(\beta_{ij}^2 - \norm{c\T_{ij} x_i}^2)} c_{ij}c\T_{ij} x_i
%                             - \frac{1}{t(\real[e^{i\phi} c\T_{ij} x_i] - \alpha_{ij})} e^{i\phi}c_{ij} \\
%                         &= \frac{1}{t} \left( \frac{c\T_{ij} x_i}{\beta_{ij}^2 - \norm{c\T_{ij} x_i}^2} 
%                             - \frac{e^{i\phi}}{\real[e^{i\phi} c\T_{ij} x_i] - \alpha_{ij}} \right)
%                         c_{ij}}
% 
%     
%     \E{}{\grad_{x_i}^2 f_i(x_i) = \frac{1}{t} \left(
%                 \frac{1}{\beta_{ij} - \norm{c\T_{ij} x_i}^2}
%                 + \frac{\norm{c\T_{ij} x_i}^2}{(\beta_{ij} - \norm{c\T_{ij} x_i}^2)^2}
%                 + \frac{1}{(\real[e^{i\phi} c\T_{ij} x_i] - \alpha_{ij})^2} \right)
%                 c_{ij} c\T_{ij}}}

    \E{}{\grad_{x_i} f_i(x_i) = \sum_j \frac{r_j}{t} c_{ij}}
    where
    \E{}{r_j = \frac{c\T_{ij} x_i}{\beta_{ij}^2 - \norm{c\T_{ij} x_i}^2} 
                - \frac{e^{i\phi}}{\real[e^{i\phi} c\T_{ij} x_i] - \alpha_{ij}},}
    and the Hessian as 
    \E{}{\grad_{x_i}^2 f_i(x_i) = \sum_j \frac{s_j}{t} c_{ij} c\T_{ij}}
    where
    \E{}{s_j = \frac{1}{\beta_{ij} - \norm{c\T_{ij} x_i}^2}
                + \frac{\norm{c\T_{ij} x_i}^2}{(\beta_{ij} - \norm{c\T_{ij} x_i}^2)^2}
                + \frac{1}{(\real[e^{i\phi} c\T_{ij} x_i] - \alpha_{ij})^2}.}

>>>>

\subsubsection{Relaxation of $f_i(x_i)$}
In order to compute $\Delta x_i$ we relax the design objectives, $f_i(x_i)$, to a differentiable, and convex form.
Specifically, the upper bound constraint is relaxed via
    \E{}{I_+(\beta_{ij} - |c\T_{ij} x_i|) \to -\frac{1}{t} \ln (\beta_{ij}^2 - \norm{c\T_{ij} x_i}^2),}
    where $t$ is a real positive scalar. The lower bound constraint is relaxed via
    \E{}{I_+(|c\T_{ij} x_i| - \alpha_{ij}) \to -\frac{1}{t} \ln (\real[e^{-i\phi_{ij}}c\T_{ij} x_i] - \alpha_{ij}),}
     where $e^{-i\phi_{ij}}$ is a phase factor on $c\T_{ij} x_i$.
The convention of $\phi_{ij} = \text{angle}(c\T_{ij} x_i)$ is often used
    to determine $\phi_{ij}$ before optimizing for $x_i$.

The gradient can now be obtained as
    \E{}{\grad_{x_i} f_i(x_i) = \sum_j \frac{r_{ij}}{t} c_{ij}}
    where
    \E{}{r_{ij} = \frac{2c\T_{ij} x_i}{\beta_{ij}^2 - \norm{c\T_{ij} x_i}^2} 
                - \frac{e^{i\phi_{ij}}}{\real[e^{-i\phi_{ij}} c\T_{ij} x_i] - \alpha_{ij}},}
    and the Hessian as 
    \E{}{\grad_{x_i}^2 f_i(x_i) = \sum_j \frac{s_{ij}}{t} c_{ij} c\T_{ij}}
    where
    \E{}{s_{ij} = \frac{2}{\beta_{ij}^2 - \norm{c\T_{ij} x_i}^2}
                + \frac{4\norm{c\T_{ij} x_i}^2}{(\beta_{ij}^2 - \norm{c\T_{ij} x_i}^2)^2}
                + \frac{1}{(\real[e^{-i\phi_{ij}} c\T_{ij} x_i] - \alpha_{ij})^2}.}
